Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-07-12 MSc-dissertation.tex
New
New para

@@

\section{Parameter estimation}
Here are some results.

\section{Model comparison}
Here are some results.

@@

\chapter{Results Analysis}

@@

\section{Discussions}
This is the place to put your conclusions about your work. You can
split it into different sections if appropriate. You may want to include
a section of future work which could be carried out to continue your
research.

@@

\chapter{Stuff which is too detailed}

Appendices should contain all the material which is considered too
detailed to be included in the main bod but which is, nevertheless,
important enough to be included in the thesis.

@@

\bibitem{ref:Tsarouchas} Tsarouchas, T.M., Wehner, D., Cavone, L., Munir, T., Keatinge, M., Lambertus, M., Underhill, A., Barrett, T., Kassapis, E., Ogryzko, N. and Feng, Y., 2018. Dynamic control of proinflam- matory cytokines Il-1$\beta$ and Tnf-$\alpha$ by macrophages in zebrafish spinal cord regeneration. Nature communications, 9(1), pp.1-17.

>>>>

\subsection{Limitations}

@@

This chapter focuses on the implementation of the ABC SMC on the proposed models. Estimation of  parameters in the proposed models is the main task of this section. ABC SMC-based models selection is another task that can be easily implemented with the parameter estimation framework.

The build and test is under \verb|Python| environment with \verb|pyABC|\cite{ref:pyabc}. Some other code e.g. shell script and \verb|R| code are also used to perform the experiments and analyse the results. Tested software and system environment can be found at Appendix A. The build and test is performed on local computers and HPC clusters available within EPCC.

\section{Parameter estimation}

\subsection{ABC SMC and model hyperparameters}

\subsection{Implementations on models}

\section{Model comparison}

@@

\chapter{Results and Discussions}

@@

\section{Discussions}

@@

\chapter{System and software environment}

\section{ABC SMC implementation}

\section{Data analysis}

@@

\bibitem{ref:Tsarouchas} Tsarouchas, T.M., Wehner, D., Cavone, L., Munir, T., Keatinge, M., Lambertus, M., Underhill, A., Barrett, T., Kassapis, E., Ogryzko, N. and Feng, Y., 2018. Dynamic control of proinflammatory cytokines Il-1$\beta$ and Tnf-$\alpha$ by macrophages in zebrafish spinal cord regeneration. Nature communications, 9(1), pp.1-17.

\bibitem{ref:pyabc} Klinger, E., Rickert, D. and Hasenauer, J., 2018. pyABC: distributed, likelihood-free inference. Bioinformatics, 34(20), pp.3591-3593.
